Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-07 providence/sections/workload.tex
unstyled sub headers
more workload

\subsection{Person-hours}
The simplest workload models are a function of just the total number of a ballots sampled. Figure~\ref{fig:avg_bals} shows the average total number of ballots sampled in our simulations for each value of $p$, which gives an estimate of the expected total number of ballots.
Figure~\ref{fig:avg_bals_ratio} gives the same number as a ratio of the Providence values.
It is straightforward to show that Providence and both forms of BRAVO collapse to the same test in the case where each round is a single ballot. Figures~\ref{fig:avg_bals} and \ref{fig:avg_bals_ratio} show that for larger stopping probabilities $p$ (i.e. larger rounds), Providence requires fewer ballots on average. In particular, the savings of Providence become larger as $p$ increases; for $p=.95$, EoR BRAVO and SO BRAVO require more than $2$ and $1.4$ times as many ballots as Providence respectively.

@@

@@

For simplicity, (and without loss of generality), we assume the per ballot cost is one, $c_b=1$. Then the per round cost $c_r$ tells us the cost of a round as a number of ballots. We begin with $c_r=1000$ as a conservative example. 
That is, we set the overhead of a round equal to the workload of sampling $1000$ ballots. Based on available data[rhode island nums], the time retrieving and analyzing each individual ballot is on the order of $75$ seconds which means that $c_r=1000$ is equivalent to roughly $20$ person-hours of workload. This corresponds to about $15$ minutes being spent per round in each of the $133$ counties of Virginia, a clearly conservative workload estimate. 
As shown in Figure~\ref{fig:with_round_cost}, lower average costs are achieved by selecting higher stopping probability; Providence achieves the lowest minimum average cost is achieved at roughly $0.7$.

@@

@@

For a more complete model, we can also introduce container-level workload. The time to sample a ballot from an entirely new box is typically much greater than to sample a ballot from an already-open box. [rhode islandd numbers shows it is abou tthis] Available election results give per-precinct granularity of vote tallies, as opposed to individual box informatoin. In Virginia, however, most precincts have a single ballot scanner whose one box has sufficient capacity for the ballots cast in that precinct anyways, and so we model the per-container workload as a per-precinct constant cost, $c_p$. In this model, the workload estimate incurs an additional cost of $c_p$ every time a precinct is sampled from for the first time in a round. That is, let $E_{pi}$ be the expected number of distinct precincts sampled from in round $i$, and let $E_p=\sum_i E_{pi}$. Then the new model is
\begin{equation}
C(E_b, E_r, E_p) = E_b c_b + E_r c_r + E_p c_p
\label{eq:round_and_precinct_cost}
\end{equation}

>>>>

\subsection{Person-hours}

Average ballots

The simplest workload models are a function of just the total number of a ballots sampled. Figure~\ref{fig:avg_bals} shows the average total number of ballots sampled in our simulations for each value of $p$, which gives an estimate of the expected total number of ballots.
Figure~\ref{fig:avg_bals_ratio} gives the same number as a ratio of the Providence values.
It is straightforward to show that Providence and both forms of BRAVO collapse to the same test in the case where each round is a single ballot. Figures~\ref{fig:avg_bals} and \ref{fig:avg_bals_ratio} show that for larger stopping probabilities $p$ (i.e. larger rounds), Providence requires fewer ballots on average. In particular, the savings of Providence become larger as $p$ increases; for $p=.95$, EoR BRAVO and SO BRAVO require more than $2$ and $1.4$ times as many ballots as Providence respectively.

@@

Round overhead

@@

For simplicity, (and without loss of generality), we assume the per ballot cost is one, $c_b=1$. Then the per round cost $c_r$ tells us the cost of a round as a number of ballots. We begin with $c_r=1000$ as a conservative example. 
That is, we set the overhead of a round equal to the workload of sampling $1000$ ballots. Based on available data\cite{RI-report}, the time retrieving and analyzing each individual ballot is on the order of $75$ seconds which means that $c_r=1000$ is equivalent to roughly $20$ person-hours of workload. This corresponds to about $15$ minutes being spent per round in each of the $133$ counties of Virginia, a clearly conservative workload estimate. 
As shown in Figure~\ref{fig:with_round_cost}, lower average costs are achieved by selecting higher stopping probability; Providence achieves the lowest minimum average cost is achieved at roughly $0.7$.

@@

Misleading probability

@@

Precinct overhead

For a more complete model, we can also introduce container-level workload. The time to sample a ballot from an entirely new box is typically greater than to sample a ballot from an already-open box. Based on a Rhode Island pilot RLA report\cite{RI-report}, this may mean that a ballot from a new container requires roughly twice the time as a ballot from an already-opened container. Typically available election results give per-precinct granularity of vote tallies, rather than individual container information. In Virginia, however, most precincts have a single ballot scanner whose one box has sufficient capacity for all the ballots cast in that precinct anyways, and so we model the per-container workload with an additional per-precinct constant cost, $c_p$. In this model, the workload estimate incurs an additional cost of $c_p$ every time a precinct is sampled from for the first time in a round. That is, let $E_{pi}$ be the expected number of distinct precincts sampled from in round $i$, and let $E_p=\sum_i E_{pi}$. Then the new model is
\begin{equation}
C(E_b, E_r, E_p) = E_b c_b + E_r c_r + E_p c_p
\label{eq:round_and_precinct_cost}
\end{equation}
